Understanding fine temporal scale evolutionary dynamics with lineage metrics

### 2018-04-03 paper.tex

%@AML:  It might be nice to wrap this section up with a little bit of a 'call to action'/'why should you care about this as a community'
%@ELD: I am in favor.
In addition to demonstrating a range of metrics that are immediately applicable and useful to digital evolution research, we intend for this work to begin a conversation within the %computational evolution
artificial life
community about how we quantify, interpret, and compare observed evolutionary histories. There has been extensive efforts to improve our ability to visualize both lineages and phylogenies [CITATIONS], which are %incredibly valuable for building intuitions and qualitatively understanding the dynamics embedded in a population's evolutionary history. However, we are unaware of efforts to formalize a suite of quantitative lineage and phylogeny-related metrics for computation evolution. Indeed, .... % people have done stuff with lineages
% - often a component of a larger experiment-specific analysis or limited to qualitative descriptions/visualizations
% - well-defined metrics not only provide valuable tools for teasing apart evolutionary dynamics, they also facilitate allow us to move away from exclusively qualitative descriptions/understandings of results ==> better quantitative understanding/statistics ==> better hypothesis testing
% - facilitate comparisons among systems. 
% - Something about activity metrics?

>>>>

%@AML:  It might be nice to wrap this section up with a little bit of a 'call to action'/'why should you care about this as a community'
%@ELD: I am in favor.
In addition to demonstrating a range of metrics that are immediately applicable and useful to digital evolution research, we intend for this work to begin a conversation within the %computational evolution
artificial life
community about how we quantify, interpret, and compare observed evolutionary histories. There has been extensive efforts to improve our ability to visualize both lineages and phylogenies [CITATIONS], which are %incredibly valuable 
indespensible 
for building intuitions and qualitatively understanding the dynamics embedded in a population's evolutionary history. However, we are unaware of efforts to formalize a suite of quantitative lineage and phylogeny-related metrics for computation evolution. Indeed, .... % people have done stuff with lineages
% - often a component of a larger experiment-specific analysis or limited to qualitative descriptions/visualizations
% - well-defined metrics not only provide valuable tools for teasing apart evolutionary dynamics, they also facilitate allow us to move away from exclusively qualitative descriptions/understandings of results ==> better quantitative understanding/statistics ==> better hypothesis testing
% - facilitate comparisons among systems. 
% - Something about activity metrics?
